A comprehensive approach to analyzing environmental data with non-detects

### 2024-06-07 Rmarkdown/README.Rmd
update readme

---
title: "A comprehensive approach to analyzing environmental data with non-detects"
author: "Benjamin F. Trueman\\* and Graham A. Gagnon"
date: "Centre for Water Resources Studies, Department of Civil & Resource Engineering, Dalhousie University, 1360 Barrington St., Halifax, Nova Scotia, Canada B3H 4R2  \n&nbsp;   \n  *Corresponding author  \nE-mail: benjamin.trueman@dal.ca    \nTel: 902.494.6070  \nFax: 902.494.3105"
output:
  word_document:
    reference_docx: paper-template.docx
bibliography: paper-references.bib
csl: environmental-science-and-technology.csl
---

@@

# Abstract

>>>>

---
output: md_document
bibliography: paper-references.bib
csl: environmental-science-and-technology.csl
---

@@

# A comprehensive approach to analyzing environmental data with non-detects
